%-------------------------
% Resume in Latex
% Author : Kunal Kumar Sahoo
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Kunal Kumar Sahoo} \\ \vspace{1pt}
    Gandhinagar, Gujarat \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 74330 64468 ~ \href{mailto:kunal.sahoo2003@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{kunal.sahoo2003@gmail.com}} ~ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{kunal-kumar-sahoo}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{Kunal-Kumar-Sahoo}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pandit Deendayal Energy University}{2021 -- 2025}
      {B.Tech in Computer Engineering (CGPA: \textbf{9.97})}{Gandhinagar, Gujarat}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}

 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Julia, Java, C, C++, Dart, MySQL, HTML, Bash} \\
     \textbf{Technologies/Frameworks}{: NumPy, Pandas, Matplotlib, Seaborn, OpenCV, Tensorflow, Keras, Mediapipe, Flask, Flutter, Arduino, Raspberry PI, Linux, GitHub, Firebase} \\
     }
     \textbf{Developer Tools}{: VS Code, Jupyter Notebooks, Google Colab, Android Studio, ViM, SolidWorks, TinkerCAD} \\
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-2pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Nyx} $|$ \emph{Tensorflow, OpenCV, ROS, Foxglove Studio}}{Semptember 2022 - Present}
          \resumeItemListStart
            \resumeItem{Developing a self-driving robot using only cameras for environment sensing.}
            \resumeItem{Have worked with several segmentation architectures like \textbf{U-Net}, \textbf{VGG} etc.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{SitRight} $|$ \emph{Python, MediaPipe, OpenCV, SQLite, Raspberry Pi}}{July 2022 - Present}
          \resumeItemListStart
            \resumeItem{Designed a \textbf{Mathematical model} for Posture classification.}
            \resumeItem{Used \textbf{OpenCV} for image preprocessing and \textbf{MediaPipe} for posture detection.}
            \resumeItem{Currently sponsored under \textbf{ORSP, PDEU} for further research and product development.}
          \resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Hand-Gesture-based-Painter} $|$ \emph{Python, NumPy, OpenCV, Mediapipe}}{May 2022}
          \resumeItemListStart
            \resumeItem{Developed a software to mimic basic drawing functionalities of MS-Paint using \textbf{hand gestures}}
            \resumeItem{Used \textbf{MediaPipe} for hand-tracking and \textbf{OpenCV} for image processing}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Face-Recognition-cum-Attendance-system} $|$ \emph{Python, NumPy, OpenCV, MySQL, DLib}}{January 2022}
          \resumeItemListStart
            \resumeItem{Developed a software for \textbf{real-time} \textbf{face recognition}.}
            \resumeItem{Used \textbf{HOG} method for face recognition from labeled data.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Face-Mask-Detection} $|$ \emph{Python, Tensorflow, OpenCV}}{January 2022}
          \resumeItemListStart
            \resumeItem{Developed a software to classify in \textbf{real-time} whether a person is wearing mask or not.}
            \resumeItem{Implemented \textbf{MobileNetV2} architecture using CNN.}
          \resumeItemListEnd 
          \vspace{-13pt}
    \resumeSubHeadingListEnd
\vspace{0 pt}

%-----------ACHIEVEMENTS-----------
\section{Achievements}
    \vspace{-2pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Grand Finalist, Azadi Ka Amrit Mahotsav Hackathon}  \emph{}}{February 2023}
          \resumeItemListStart
            \resumeItem{Participated in the grand finale round of the hackathon organized by\textbf{ SSIP, Govt. of Gujarat}}
            \resumeItem{Developed a website using \textbf{ReactJS}, \textbf{Flask} and \textbf{MySQL} to provide a digital incubation-cum-ecosystem for startups.}
          \resumeItemListEnd
          \vspace{-13pt}

        \resumeProjectHeading
          {\textbf{Merit, National Analytics Challenge}  \emph{}}{January 2023}
          \resumeItemListStart
            \resumeItem{Participated in Quiz conducted by \textbf{XLRI, Jamshedpur} in the domains of \textbf{Data Analytics}}
            \resumeItem{Secured rank \textbf{12} out of \textbf{600+} registered participants}
          \resumeItemListEnd
          \vspace{-13pt}
        
        \resumeProjectHeading
          {\textbf{Grand Finalist, EnCode@IIT Guwahati}  \emph{}}{January 2023}
          \resumeItemListStart
            \resumeItem{Secured \textbf{3rd} position in the grand finale round of the EnCode, a hackathon organized by\textbf{IIT Guwahati} sponsored by \textbf{Bosch}}
            \resumeItem{Developed a \textbf{Deep Learning model} for \textbf{Road segmentation} and \textbf{3-D Box Bounding} using for autonomous vehicles using \textbf{Cityscape Dataset}}
          \resumeItemListEnd
          \vspace{-13pt}

          \resumeProjectHeading
          {\textbf{Merit, Kharagpur Data Science Hackathon 2022}  \emph{}}{December 2022}
          \resumeItemListStart
            \resumeItem{Participated in Data Science Hackathon conducted by \textbf{IIT Kharagpur}}
            \resumeItem{Secured rank \textbf{18} out of \textbf{755} registered teams}
          \resumeItemListEnd
          \vspace{-13pt}
 \resumeSubHeadingListEnd
 \vspace{1}
 
%-----------EXPERIENCE-----------
\section{Experience}
    \vspace{1pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SLoP 2.0, DA-IICT}{Oct 2022 -- Nov 2022}
      {Contributor}{Remote}
      \resumeItemListStart
        \resumeItem{Worked on the project \textbf{Finding data from Permanent Shadowed Regions}}
        \resumeItem{Developed a Python script to generate \textbf{.tif images} from \textbf{OHRC} data.}
        \resumeItem{Tech-stack: Python (NumPy, Pandas, Matplotlib, Scikit-learn), OpenCV}
      \resumeItemListEnd

      \resumeSubheading
      {GDSC Student Chapter, PDEU}{Sept 2022 -- Present}
      {Team member, AI/ML}{Remote}
      \resumeItemListStart
        \resumeItem{Developing an application for \textbf{real-time OCR} and \textbf{translator} for regional texts.}
        \resumeItem{Tech-stack: GCP, AutoML, Google ML APIs}
      \resumeItemListEnd

    \resumeSubheading
      {Encode, PDEU}{August 2022 -- Present}
      {Core committee member, App Development, AI/ML}{Gandhinagar, Gujarat}
      \resumeItemListStart
        \resumeItem{Working on a recommendation system using \textbf{Deep learning} and \textbf{Clustering} from categorical data.}
        \resumeItem{Developed a \textbf{mobile application} for the Quiz club of university.}
        \resumeItem{Tech-stack: Tensorflow, Scikit-learn, MySQL, Flutter, Git, Firebase}
    \resumeItemListEnd
    
    \resumeSubheading
      {Cretus, PDEU}{August 2021 -- Present}
      {Technical member}{Gandhinagar, Gujarat}
      \resumeItemListStart
        \resumeItem{Built a working half-scale prototype of \textbf{Perseverance rover} and live-streamed camera feed using Python.}
        \resumeItem{Also developed, competitive line followers, obstacle avoiders and micromouses for robotics competition.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{4pt}

\end{document}
